Integrated farming and global warming mitigation in Brazil

### 2022-09-27 manuscript/manuscript.qmd
Add text to the methods section.

The above ground carbon will be calculated by estimates of tree growth and litter accumulation, and will be based on empirical models (ordinary least squares linear regression). The above ground carbon accumulation will be dependent on climatic variables, the species used in the ICLF system, and the population of each component of the integrated system.

@@

@@

>>>>

The above ground carbon will be calculated by estimates of tree growth and litter accumulation, and will be based on empirical models (ordinary least squares linear regression or random forest). The above ground carbon accumulation will be dependent on climatic variables, the species used in the ICLF system, and the population of each component of the integrated system.

@@

The food and fiber productivity will be calculated separately for each component of ICLF. The components are the trees, the annual crops, the pasture and the livestock.

The estimations of productivity will be performed by empirical models (ordinary least squares linear regression or random forest). They will be based on data gathered from the systematic review, and will be dependent on climatic variables, species used in each component, and the population numbers.

The economic revenue estimations will account for costs and income related to the ICLF implementation.

The costs to implement the ICLF systems will be based on management practices gathered by the systematic
review, as also external sources when necessary. The income will be calculated over the productivity of each component of the ICLF system. The prices off inputs and outcomes will be corrected by inflation projections.

@@

The critical analysis will expand the interpretation of the suitability of the expansion of ICLF as a mean to curb global warming. This will be done by putting the ICLF in context of some subjects:

* The impact of the ICLF expansion in Brazil is important when comparing it with estimations of gross national emissions? What are the areas where the ICLF can actually help in decreasing emissions?

* What are possible social impacts of the stimulation of ICLF adoption? Will it decrease social inequality in rural areas? Will it play a role in mitigating damage caused by climate change?

* Nature based solutions or human based solutions? Do they complement each other or do they compete?

* What are the consequences of focusing on increasing carbon removals rather than decreasing gross emissions? And how is this being addressed in public policies.

To discuss the points above, a targeted review will be performed. The targeted review will be conducted by actively searching for digital content of various nature to seek information about the questions. It contrasts the systematic review since there will be no formal strategy of literature search.

The use of a narrative discussion will expand the scope of the project, avoiding to drawn all the conclusions solely on quantitative estimates, and to put all the generated results in contexts of a bigger scenario.
